Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-06-28 sm.tex
[SM] Fix ref in pdf, include numbers in plot

\begin{figure}
  \includegraphics[width=8.5cm]{imgs/simcool_no_scatter.pdf}
  \caption{Simulated ground state population as a function of cooling cycles without
    technical imperfections \label{f-no-scatter}}
\end{figure}

\begin{figure}
  \includegraphics[width=8.5cm]{imgs/simcool_real.pdf}
  \caption{Simulated ground state population as a function of cooling cycles including effect of
    off-resonant scattering from all beams and OP misalignment\label{f-real}}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=8.5cm]{imgs/simcool_no_scatter.pdf}
  \caption{Simulated ground state population as a function of cooling cycles without
    technical imperfections. The ground state probability reaches $>99\%$. \label{f-no-scatter}}
\end{figure}

\begin{figure}
  \includegraphics[width=8.5cm]{imgs/simcool_real.pdf}
  \caption{Simulated ground state population as a function of cooling cycles including effect of
    off-resonant scattering from all beams and OP misalignment.
    For this particular sequence, the ground state probability saturates $\approx88\%$.
    \label{f-real}}
\end{figure}
